### 2014-06-23 inst/wtc-finland/manuscript.Rmd
...

```{r straight-line-distance-error, fig.height=5}
ss <- SimulationStudy$new(response="Intensive")$newInstance(context=context)
tracks <- ss$loadTracks(iteration=as.integer(1))
tracks$tracks <- subset(tracks$tracks, id == 1 & year == 2001 & month == 1 & day %in% c(2,3))
intervals <- MovementSampleIntervals$new(study=ss)
thinnedTracks <- intervals$getThinnedTracksSampleIntervals(tracks=tracks)

>>>>

```{r straight-line-distance-error, fig.height=5}
ss <- SimulationStudy$new(response="Intensive")$setup(context=context)
tracks <- ss$loadTracks(iteration=as.integer(1))
tracks$tracks <- subset(tracks$tracks, id == 1 & year == 2001 & month == 1 & day %in% c(2,3))
intervals <- MovementSampleIntervals$new(study=ss)
thinnedTracks <- intervals$getThinnedTracksSampleIntervals(tracks=tracks)
